---
title: "Lab Wk 8"
author: "Maddie Julian"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load Packages
```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
library(corrplot)
```

###Column graph of Texas oil spills

```{r}
oil_spills <- read_csv("oil_spills.csv")

df<- oil_spills %>% 
  filter(`Accident State` == "TX" & `Accident Year`<2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))#apply one or more functions to a data set; creating new value called Loss
#View(df)

colnames(df) <- c("Year", "Loss")

ggplot(df, aes(x=Year, y=Loss)) +
  geom_col()
```


###Leaflet plot of spill locations in TX in 2016

```{r}
df_loc <- oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year`=="2016") %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc)<- c("latitude", "longitude", "net_loss")

oil_sf <- st_as_sf(df_loc, coords= c("longitude", "latitude"), crs = 4326) #convert current df info into simple feature spatial data

leaflet(oil_sf) %>% 
  addTiles() %>%  #base graph
  addMarkers()

```


##tmap plot with Texas state shapefile

```{r}
states <- st_read(dsn = ".", layer = "states")
#can now treat this info liek a data fram and will keep geometry as polygons etc

tex_border <- states %>% 
  filter(STATE_NAME == "Texas") %>%  #filter by column where state name matches texas
  st_transform(4326) #change the crs number for epsg value (matches oil spill points that we have)

plot(tex_border)
#plots all 5 non geometry column

#but we want to plot the state with points on top of top of it

tm_shape(tex_border) +
  tm_polygons()+
  tm_shape(oil_sf)+
  tm_dots(size = 0.3)
  
  #then want to ask, does this point pattern follow poisson distribution? is it randomly spatially distributed?
```

###Convert the data to spatial points patterns (combination of point data and the bounding window -- used to evaluate the points within it)

```{r}

spill_sp <- as(oil_sf, "Spatial") #convert oil_sf back to spatial data frame
spill_ppp <- as(spill_sp, "ppp") #convert new df to point pattern


tx_sp <- as(tex_border, "Spatial")
tx_owin <- as(tx_sp, "owin") #make this border the outer window for ppp

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin) #corresponding long and lats, also window
#4 points are rejected b/c they are outside the boundaries of the state

```

###A density plot:
```{r}
plot(density(all_ppp, sigma = 0.4)) #sigma means radius of the bubbles
```

###Quadrat test for spatial evenness

```{r}
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5) #horizontally want there to be a total of 5 regions, and 5 vertically(breaks up whole state of texas into 5 regions in each direction)
oil_qt

#testing a null hypothesis of csr - randomness
#b/c of outcome, you would reject null; say that data is not spatially evenly distributed -- see sig p value

plot(all_ppp)
plot(oil_qt, add = TRUE, cex = 0.4)

#numbers in boxes
#upper right = expected
#upper left = actual
#sd measure of how different from the expected
```

###G-Function for Nearest Neighbor Analysis

```{r}
r <- seq(0, 1, by = 0.01) #lag

oil_gfun <- envelope(all_ppp, fun = Gest, r = r, nsim = 100) #nsim means run 100 simulations

#THEO: THEORETICAL VALUES BASED ON SIMULATIONS

ggplot(oil_gfun, aes(x = r, y = obs))+
  geom_line(color = "black")+
  geom_line(aes(x = r, y = theo), color = "red")
#our obs data has a higher proportion of point pairs with nearest neighbors at shorter distances compared to csr data
#*on average our data has nearest neighbor thats closer than we would expect with csr
```

#Nearest neighbor using the L-fucnction (Ripley's K function but standardized)

```{r}
r2 <- seq(0,3, by = 0.5)

oil_lfun <- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE) #looks at every point and makes increasing bubbles around it until it include every point that exists; so we do 20 simulations b/c it takes a long time

ggplot(oil_lfun, aes(x = r2, y = obs))+
  geom_line(color = "black")+
  geom_line(aes(x = r2, y = theo, color = "red"))
```

